---
title: "simulation"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)

## Set Global Options 
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6, 
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


**Understand the properties of your analysis in repeated sampling.**

**Does statistic do what it's supposed to do?**


# Let's simulate:

I have a function 

```{r}
sim_mean_sd = function(samp_size, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(samp_size, mean = mu, sd = sigma),
  )
  
  #returns 
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

I can "simulate" by running this line 

```{r}
sim_mean_sd(30)
```


# Let's simulate a lot

Let's start with a for loop.

```{r}

#100 times -> I have gone out in to the universe and asked the universe to give me a sample size 30, with a true mean 3 and true standard deviation 40, from a normal distribution 

output = vector("list", length = 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(samp_size = 30)
}

bind_rows(output)
```


Let's us a loop function

```{r}

#using rerun() function

sim_results =
  rerun(100, sim_mean_sd(samp_size = 30)) %>%
  bind_rows()

#generating a list, similar to output 
```


Let's look at results

# distribution of the sample mean across 100 replications of this simulation 
```{r}

# population SD is sigma_hat divided sqrt of sample size 

sim_results %>%
  ggplot(aes(x = sigma_hat)) + geom_density()

sim_results %>%
  summarise(
    avg_sample_mean = mean(mu_hat),
    sd_sample_mean = sd(mu_hat)
  )
```



## Let's try other sample sizes

```{r}
n_list = 
  list(
    "n = 30" = 30,
    "n = 60" = 60,
    "n = 120" = 120,
    "n = 240" = 240
  )

output = 
  vector("list", length = 4)


output[[1]] = rerun(100, sim_mean_sd(samp_size = n_list[[1]])) %>% bind_rows()
output[[2]] = rerun(100, sim_mean_sd(samp_size = n_list[[2]])) %>% bind_rows()
```



```{r}
for (i in 1:4) {
  
  output[[i]] =
    rerun(100, sim_mean_sd(samp_size = n_list[[i]])) %>% 
    bind_rows()
  
}
```



```{r}
tibble(
  sample_size = c(30, 60, 120, 240)
) %>% 
  mutate(
    output_lists = map(.x = sample_size, ~ rerun(100, sim_mean_sd(.x)))
  )
```


